---
title: "Video_DataPrep"
output: html_document
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

# PACKAGES
```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(openxlsx)
library(ggplot2)
library(psych)
library(stringr)
library(pals)
library(oce) # To estimate water density
library(reshape2)
library(readxl)

set.seed(6) # At one point I "randomly "chose" stations within some Rstations. This makes sure that the random selection stays equal to allow replicability among us. 
```

# PATHS and other funcitons
```{r, message=FALSE, warning=FALSE}
HI_user<-"a39495"

PathScripts<-paste0("C:/Users/",HI_user,"/Havforskningsinstituttet/MAREANO Biotope modelling - General/VideoData/Scripts/")
PathInputData<-paste0("C:/Users/",HI_user,"/Havforskningsinstituttet/MAREANO Biotope modelling - General/VideoData/Input/")
PathOutput<-paste0("C:/Users/",HI_user,"/Havforskningsinstituttet/MAREANO Biotope modelling - General/VideoData/Output/")
PathTaxonary<- paste0("C:/Users/",HI_user,"/Havforskningsinstituttet/Video analysis lab - Reference List/Taxonary.xlsx")

source("MY_TaxonomicFromWormsDF.r")
source("VME_Spp.r")
```


```{r}
# Thresholds:
length_lower <- 190 
length_upper <- 300 
bad_vision<- 0.5
MinOTUs<- 3 # Min number of species in station
MinSightings<- 20 #Min number of sighting for a species to be included
MinDepth<- -100
```

## EXTRAS
# Land geography
```{r, message=FALSE}
load(paste0(PathInputData,"worldMap.rda"))
ggworldMap<-fortify(worldMap)
```
# LOAD DATA
## -Trawling
Loads trawling data
```{r, warning=FALSE, message=FALSE}
if(FALSE){
source(paste0(PathScripts,"LoadHarvestingSpatial.r"))
}
load(paste0(PathInputData,"rHarvestEffort_raster.rda")) # loads rHarvestEffort
```

## -ENVIRONMENTAL LOAD
```{r, warning=FALSE}
env_orig <- read.csv(paste0(PathInputData,"envData_2023-07-21.csv")) %>% as.data.frame
env_orig<-unique(env_orig)
env_orig[sapply(env_orig, is.character)] <- lapply(env_orig[sapply(env_orig, is.character)], as.factor)

samp_info <- read.csv(paste0(PathInputData,"sample_info.csv")) %>% as.data.frame
samp_info<-samp_info[!(duplicated(samp_info$SampID)),]
env_orig<-merge(env_orig, samp_info[,1: which(colnames(samp_info) == "no_vision"),], by = "SampID", all.x = TRUE)
```

##Sedim extra
# Adds new sediment (percent mud, sand, gravel) based on video observation 
```{r, warning=FALSE}
sed_info <- read.csv(paste0(PathInputData,"sedimMeans.csv")) %>% as.data.frame
sed_info<-dcast(SampID ~Substrate , value.var = "mean_percent", data = sed_info)
sed_info[2:36][is.na(sed_info[2:36])]<-0
sed_info$SUM<-rowSums(sed_info[,c(2:ncol(sed_info))], na.rm = TRUE)
sed_info[2:36]<-(sed_info[2:36]/sed_info$SUM)*100
sed_info$SAND<-rowSums(sed_info[,c("Sand","Sand_with_biomaterial","Sand_with_shells","Sand.with.shells")], na.rm = TRUE) + 
  sed_info[,c("Gravelly.sand")] * 0.75 + 
  sed_info[,c("Muddy sand")] * 0.65 + 
  rowSums(sed_info[,c("Sandy mud","Sandy_mud", "Sandy.mud")], na.rm = TRUE)* 0.35
sed_info$MUD<-rowSums(sed_info[,c("Clay", "clay (outcropping)", "Clay_spicules","Mud")], na.rm = TRUE) + 
  rowSums(sed_info[,c("Sandy mud","Sandy_mud", "Sandy.mud")], na.rm = TRUE) * 0.65 +
  sed_info[,c("Muddy sand")] * 0.35
sed_info$LopheliaDEAD<-rowSums(sed_info[,c("Coral rubble", "Coral_rubble", "Coral.rubble", "Dead lophelia", "Dead_lophelia","lophelia rubbel", "Lophelia rubbel", "Lophelia_rubble")], na.rm = TRUE)
sed_info$LopheliaLIVE<-rowSums(sed_info[,c("Live lophelia", "Live_lophelia", "Live.Lophelia")], na.rm = TRUE)
sed_info$GRAVEL<-rowSums(sed_info[,c("Pebble", "Shellsand")], na.rm = TRUE)
sed_info$LopheliaLIVE<-rowSums(sed_info[,c("Live lophelia", "Live_lophelia", "Live.Lophelia")], na.rm = TRUE)

env_orig<-merge(env_orig, sed_info, by = "SampID", all.x = TRUE)

env_orig<-env_orig %>%
  dplyr::select(-("X.1")) %>%
  unique(.)

env_orig$sand2<-ifelse(is.na(env_orig$SAND), env_orig$sand, env_orig$SAND)
env_orig$mud2<-ifelse(is.na(env_orig$MUD), env_orig$mud, env_orig$MUD)

## Removing some env variables that I dont use and which were giving issues because they contain NAs
#env_orig <- env_orig %>% dplyr::select(-c(spd_std, slope9, BO22_lightbotltmax_bdmean, BO22_lightbotltmin_bdmean, BO22_lightbotmean_bdmean, BO22_lightbotrange_bdmean))
```

## -Bio
```{r, warning=FALSE}
otu_orig <- read.csv(paste0(PathInputData,"species_densities.csv")) %>% as.data.frame
otu_orig <- dcast(otu_orig, SampID ~ clean_taxonomy, value.var="density_n100m2")
otu_orig[is.na(otu_orig)]<-0
# These clarifications help prevent issues later when pulling info from worms about taxonomy
colnames(otu_orig)[which(colnames(otu_orig) == "Pennatulacea")]<-"Pennatuloidea"
colnames(otu_orig)[which(colnames(otu_orig) == "Cephalopoda benthic")]<-"Cephalopoda"
```

## - Taxon
```{r, warning=FALSE}
Taxonary<-read.xlsx(PathTaxonary , sheet = 1)
# Some functions later on might change certain characters
Taxonary$Reference.List2 <-gsub(";", ".", Taxonary$Reference_List) 
Taxonary$Reference.List2 <-gsub("[ /]", "_", Taxonary$Reference.List2)
# These clarifications help prevent issues later when pulling info from worms about taxonomy
Taxonary[Taxonary$Reference_List == "Pennatulacea",'Reference_List']<-"Pennatuloidea"
Taxonary[Taxonary$Reference_List == "Cephalopoda benthic",'Reference_List']<-"Cephalopoda"
```

Filter out taxa:
- Small taxa
- Plants and other non-animals
```{r, warning=FALSE}
otu_orig<-otu_orig[,c(TRUE, colnames(otu_orig)[-1] %in% Taxonary[
  Taxonary$Size_class %in% c("OK", "Detailed") & 
    Taxonary$Specificity<4 & 
    Taxonary$Object_type == "Organism" & 
    Taxonary$Ecosystem_section != "Pelagic" &
    !(Taxonary$Grouping_taxon_biotope %in% c("Algae", "Bacteria", "Biota", "Foraminifera","Bryozoa")) ,'Reference_List'])]
```

# JOIN DATASETS 
Join the different data sets to make them match and filter out some stations based on:
- minimum length
- minimum vision 
- 2006 cruise removed 
 +(Maybe part of 2019115 too? cause it has many very close stations within Kongsfjorden which produce a lot of noise in the spatial pattern)
- stations that produced errors in the latent autocorrelation estimation (neighbouring stations with very different species patters)
```{r, warning=FALSE}
joinedDat<- left_join(otu_orig,env_orig, by="SampID")
joinedDat<-joinedDat[!is.na(joinedDat$SampID),]
joinedDat<-joinedDat[joinedDat$SegLengthM>length_lower & joinedDat$SegLengthM < length_upper,]
joinedDat<-joinedDat[is.na(joinedDat$no_vision) | rowSums(joinedDat[,c('no_vision','poor_vision')], na.rm = TRUE) < bad_vision | is.na(joinedDat$poor_vision),]
joinedDat<-joinedDat[joinedDat$cruise_no != "2006612",]

#!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
#!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
joinedDat<-joinedDat[!(joinedDat$cruise_no == "2019115" & joinedDat$x_coord> 400000 & joinedDat$y_coord>8500000),]
#Check again!
#!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
#!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

# Instead of taking random segement from long transects, we now select the first segment of any transect 
temp_01<-joinedDat[!(str_sub(joinedDat$SampID,-2,-1) %in% c("06","05","04","03","02","00" ,"_D", "_C")),]
joinedDat<-joinedDat[!(str_sub(joinedDat$SampID,-2,-1) %in% c("06","05","04","03","02","01", "_D", "_C")),]
joinedDat<-rbind(joinedDat, temp_01[!(temp_01$VL %in% joinedDat$VL),])

joinedDat<-joinedDat[!is.na(joinedDat),]
#Takes one random 200m transect from each station
joinedDat<-joinedDat %>%
  dplyr::group_by(VL)%>%
  dplyr::slice_sample(n=1) %>%
  ungroup()

# Removes stations with missing key environmental data (needed for predictions) 
joinedDat <- joinedDat[complete.cases(joinedDat[, c("x_coord", "y_coord","cruise_no","mud2","sand2", "Tmean_Robinson","bathy", "BO22_dissoxltmin_bdmean")]), ]

joinedDat<-joinedDat[joinedDat$bathy <= MinDepth,]
# Stations that continued to give issue on the spatial analyeses
StationRefs <- read.csv(paste0(PathInputData,"reference.csv"), sep = "|") %>% as.data.frame

joinedDat<-joinedDat[!(joinedDat$VL %in% c('2340', '544', '254', '829','606', '162', StationRefs[!is.na(StationRefs$reason_excluded),'nSampleNumber'])),]
```

# SEPARATE joineddat
Separate the now matching datasets (joinedDat -> otu_sort + env_sort)
```{r, warning=FALSE}
otu_sort<- joinedDat %>% 
  dplyr::select(c(1,2:which(colnames(joinedDat)==names(otu_orig)[ncol(otu_orig)])))

envCompl<-env_sort<-joinedDat %>% 
  dplyr::select(c(1, (which(colnames(joinedDat)==names(otu_orig)[ncol(otu_orig)])+1):ncol(joinedDat)))

envCompl$Trawling<-extract(rHarvestEffort, envCompl[,c('x_coord', 'y_coord')]) # Add the trawling data created before
```

### Data cleaning
Remove  otu
```{r}
# Remove species with 0 records
otuCompl<-otu_sort %>% select_if(~ !is.numeric(.) || sum(.) != 0) 

#Remove species
otuCompl<-otuCompl[,-which(colnames(otuCompl) %in% c("Cup coral" #, # This one gets lost in the taxonomic functions because it is not associated to any toxonomic valid name
))]

 colnames(otuCompl) <-gsub(";", "_", colnames(otuCompl))
 colnames(otuCompl) <-gsub("[ /]", "_",  colnames(otuCompl))
 colnames(otuCompl)<-ifelse(str_sub( colnames(otuCompl),-3,-1) != "sp.", gsub("[.]", "_",  colnames(otuCompl)),  colnames(otuCompl))  

```

Results in a data set that contains information on which species could be summed with otus of coarser resolution. This is done to improve predictions of those coarser resolution otus, which in turn might help improve prediction strength on the finer resolutions

```{r}
#Takes otuCompl
source(paste0(PathScripts,"TaxonomyAggregate.r")) 
# Gives Taxonomic_DF_Groups
levels(Taxonomic_DF_Groups$Species)[levels(Taxonomic_DF_Groups$Species) == "Echinoidea irregular"] <- "Irregularia"
levels(Taxonomic_DF_Groups$Species)[levels(Taxonomic_DF_Groups$Species) == "Echinoidea regular"] <- "Carinacea"
```

Sums observations of finer resoltuions to the higher resolutions
```{r}
MultiSpecies <- c("Ceramaster_Hippasterias", "Porania_Poraniomorpha" ,"Bythocaris_Boreomysis", "Lycodonus_Lycenchelys_Lumpenus", "Lycodonus_Lycenchelys", "Phakellia_Axinella", "Geodia_Stryphnus", "Geodia_Stelleta")
otuCompl_Sum<-otuCompl
for(i in 2:ncol(otuCompl)){
  
  TargetSp<-colnames(otuCompl)[i]
  TargetSp<-ifelse(str_sub(TargetSp,-3,-1) == "sp.", str_sub(TargetSp,-str_length(TargetSp),-5), TargetSp)
  
  # otus indicating multiple possible species are flaged and treated different to simple coarser resolutions otus
  if(TargetSp %in% MultiSpecies){
    MultiSp<-unlist(str_split(TargetSp, "_"))    
    if(any(MultiSp %in% "Hippasterias")){MultiSp<- c("Ceramaster", "Hippasteria")}
    RelatedSp<-Taxonomic_DF_Groups %>% dplyr::select(which(colnames(Taxonomic_DF_Groups) == "Genus"):ncol(Taxonomic_DF_Groups)) %>% filter_all(any_vars(. %in% MultiSp))
    
  }else{
    if(TargetSp == "Echinoidea_regular"){TargetSp<-"Carinacea"}
    if(TargetSp == "Echinoidea_irregular"){TargetSp<-"Irregularia"}
    
    RelatedSp<-Taxonomic_DF_Groups %>% dplyr::select(which(colnames(Taxonomic_DF_Groups) == "Species"):ncol(Taxonomic_DF_Groups)) %>% filter_all(any_vars(. %in% c(TargetSp)))
  }
  
  OtherSp<-RelatedSp$Species[RelatedSp$Species != TargetSp]
  if(length(OtherSp) == 0){next}
  
print(paste0(c(TargetSp,"<--- ", paste(OtherSp, collapse="; ")) , collapse= ""))  

  temp_sp <-gsub(";", ".", c(colnames(otuCompl)[i],paste(OtherSp)))
  temp_sp <-gsub("[ /]", "_", temp_sp)
  temp_sp<-ifelse(str_sub(temp_sp,-2,-1) == "sp", paste0(temp_sp, "."), temp_sp)  
  
  otuCompl_Sum[,paste0(TargetSp, "_Summed")]<-rowSums(otuCompl_Sum[,which(colnames(otuCompl_Sum) %in% temp_sp)])
}
otuCompl_Sum<-otuCompl_Sum %>% dplyr::select(-c(Bythocaris_Summed)) 
otuCompl_Sum$Porania_Summed <- rowSums(otuCompl_Sum[,which(colnames(otuCompl_Sum) %in% c("Porania_pulvillus", "Porania_sp."))])
```

Grouping of additional entries based on morphology/color?
```{r}
# PORIFERA
Taxonary[Taxonary$Reference_List %in% c("Porifera encrusting;bluegrey", "Porifera encrusting;brown","Porifera encrusting;green","Porifera encrusting;grey","Porifera encrusting;orange","Porifera encrusting;purple", "Porifera encrusting;red","Porifera encrusting;white", "Porifera encrusting;yellow", "Halichondria sp."), 'Analysis_name']<-"Porifera encrusting"
Taxonary[Taxonary$Reference_List %in% c("Porifera medium;white","Porifera medium;yellow"), 'Analysis_name']<-"Porifera medium"
Taxonary[Taxonary$Reference_List %in% c("Porifera small;irregular","Porifera small;orange","Porifera small;white","Porifera small;yellow", "Porifera small;spikey", "Porifera small;green", "Porifera urn", "Grantia compressa"), 'Analysis_name']<-"Porifera small"
Taxonary[Taxonary$Reference_List %in% c("Porifera small;round yellow", "Porifera cupcake",  "Porifera_window", "Tetilla sp.", "Tentorium semisuberites"), 'Analysis_name']<-"Porifera small round"
Taxonary[Taxonary$Reference_List %in% c("Porifera lollipop", "Porifera lily", "Halichondria sp.", "Hyalonema sp.","Sycon stalked", "Sycon sp.", "Hyalonema sp."), 'Analysis_name']<-"Porifera small;stalked"
Taxonary[Taxonary$Reference_List %in% c("Porifera bat"), 'Analysis_name']<-"Porifera erect"
Taxonary[Taxonary$Reference_List %in% c("Porifera white bush"), 'Analysis_name']<-"Porifera branched"
Taxonary[Taxonary$Reference_List %in% c("Porifera fan;big","Porifera fan;white", "Porifera fan;small","Plicatellopsis bowerbanki"), 'Analysis_name']<-"Porifera fan"
Taxonary[Taxonary$Reference_List %in% c("Primnoa resedaeformis;impacted"), 'Analysis_name']<-"Primnoa resedaeformis" 
Taxonary[Taxonary$Reference_List %in% c("Paragorgia arborea;impacted"), 'Analysis_name']<-"Paragorgia arborea"
Taxonary[Taxonary$Reference_List %in% c("Porifera brown papillae"), 'Analysis_name']<-"Polymastiidae" # "Polymastia sp.", "Weberella bursa","Polymastia grimaldii"
 
Taxonary[Taxonary$Reference_List %in% c("Drifa_glomerata", "Duva_florida","Duva_sp.","Gersemia_rubiformis"), 'Analysis_name']<-"Nephtheidae"


FixThis<-c("Porifera encrusting","Porifera medium" ,"Porifera small","Porifera small round","Porifera small;stalked","Porifera small;stalked","Porifera erect","Porifera branched","Polymastiidae","Porifera fan","Primnoa resedaeformis" ,"Paragorgia arborea", "Nephtheidae")

for(i in 1:length(FixThis)){
  From<-Taxonary[!is.na(Taxonary$Analysis_name) & Taxonary$Analysis_name %in% FixThis[i],'Reference.List2']
  To<-Taxonary[Taxonary$Reference_List == FixThis[i],'Reference.List2']
  
  if(any(colnames(otuCompl) %in% From)){
    if(any(colnames(otuCompl) %in% To)){
      otuCompl[,To]<-rowSums(otuCompl[,which(colnames(otuCompl) %in% c(To, From))]) # sums densities of all species with same "analyses name"
    }
  }
}
```

"otuCompl_Sum" currently contains columns with the unsummed and the summed coarser taxonomic resolutions. We  remove the unsummed. We also remove these unsumed in the "otuCompl" (which had the summed morphotypes) data frame and combine the columns to end up with a data frame containing summed morphotypes and summed taxonomies.
```{r}
# Taxonomic resolutions summed dataset 
tempdf<-otuCompl_Sum[,which(!(colnames(otuCompl_Sum) %in% colnames(otuCompl)))]
colnames(tempdf)<- str_sub(colnames(tempdf),-str_length(colnames(tempdf)) ,-8) # Removeds the "_Summed" part of the string

# Morphotypes fix summed dataset 
otuCompl<-otuCompl[, which(!(colnames(otuCompl) %in% c(colnames(tempdf),paste0(colnames(tempdf),"_sp."))))]

# Merge fixed datasets
otuCompl<-cbind(otuCompl, tempdf)
#Remove old morphotypes
otuCompl<-otuCompl[,which(!(colnames(otuCompl) %in% c("Actiniaria.red","Actiniaria.violet","Actiniaria_buried.redish","Actiniaria.orange","Actiniaria.pink","Actiniaria.white","Actiniaria.yellow",
                                                      "Cerianthidae.dark","Cerianthidae.violet",
                                                      "Asteroidea.orange", "Asteroidea.white",
                                                      "Bryozoa_calcareous_branched","Bryozoa_coral",      
                                                      "Porifera_encrusting.bluegrey","Porifera_encrusting.green","Porifera_encrusting.grey","Porifera_encrusting.orange","Porifera_encrusting.purple", "Porifera_encrusting.white", "Porifera_encrusting.yellow",  "Porifera_fan.white","Porifera_medium_round","Porifera_medium.white" ,"Porifera_medium.yellow", "Porifera_small.irregular","Porifera_small.round_yellow", "Porifera_small.white", "Porifera_small.yellow", "Porifera_bat", "Porifera_lollipop", "Porifera_lily")))]
```


Now, after having fixed all the species entries, we will remove those species with too few occurrences

Subsets based on thresholds:
-Species with a minimum number of occurrences
-Stations with the minimum number of species and 
```{r}
# Removes species with less than "MinSightings" that are not VMEs
Sp_sel <- c(TRUE, colSums(otuCompl[, -c(1)]>0) > MinSightings)
Sp_sel[which(names(Sp_sel) %in% c(ALL_vme))]<-TRUE

stations_sel <- rowSums(otuCompl[, -c(1)]>0) > MinOTUs

otuSel <- otuCompl[stations_sel, Sp_sel]
envSel <- envCompl[stations_sel, ]

envSel$swDensRob_avs<-swRho(salinity=envSel$Smean_Robinson,
                            temperature=envSel$Tmean_Robinson,
                            pressure=(envSel$bathy*-1),
                            eos="unesco")

envSel<-envSel[ , colSums(is.na(envSel))==0] #Remove environmental variables with NAs
envSel$SampID<-as.factor(envSel$SampID)
```


# SPLITS
```{r, warning=FALSE, fig.width= 10,fig.height = 10}
envSel_split<-list()
otuSel_split<-list()

StudyRegion<-envSel[,  'SampID']
envSel_split[["All"]]<-envSel[envSel$SampID  %in% StudyRegion$SampID,]
otuSel_split[["All"]]<-otuSel[otuSel$SampID %in% StudyRegion$SampID,]

PointSizes<- 1

ggplot()+
  geom_point(data = env_orig[ env_orig$SampID %in% otuCompl[rowSums(otuCompl[, -c(1)]>0) <= MinOTUs,'SampID'],], aes(x_coord, y_coord, color = "Few otus"), size = PointSizes)+
  geom_point(data = env_orig[rowSums(env_orig[,c('no_vision','poor_vision')], na.rm = TRUE) > 0.5,], aes(x_coord, y_coord, color = "Poor vision"), alpha = 0.5, size = PointSizes)+
  geom_point(data = env_orig[env_orig$SegLength< length_lower,], aes(x_coord, y_coord, color = "Too short"), alpha = 0.5, size = PointSizes)+
  geom_point(data = env_orig[env_orig$SegLength> length_upper,], aes(x_coord, y_coord, color = "Too long"), alpha = 0.5, size = PointSizes)+

  geom_point(data = env_orig[env_orig$bathy > MinDepth,], aes(x_coord, y_coord, color = "Too shallow"), alpha = 0.5, size = PointSizes)+
  geom_point(data = env_orig[env_orig$cruise_no  == "2006612" | (env_orig$cruise_no == "2019115" & env_orig$x_coord> 400000 & env_orig$y_coord>8500000),], aes(x_coord, y_coord, color = "2006 cruise \n& Kongfjord"), alpha = 0.5, size = PointSizes)+
  geom_point(data = envSel_split[["All"]], aes(x_coord, y_coord, color = "Not excluded"), size = PointSizes)+
    geom_map(data =  ggworldMap, map = ggworldMap, aes(long, lat, map_id = id), fill = "#ddb892", alpha = 0.4)+
  theme_void()+
  scale_color_manual(name='Stations excluded',
                     breaks=c('Poor vision', 'Too short','Too long', 'Too shallow', '2006 cruise \n& Kongfjord','Not excluded', "Few otus"),
                     values=c('Poor vision' = "#e9c46a", 'Too short' = "#e76f51", 'Too long' = "#9c89b8", 'Too shallow' = "#2a9d8f", '2006 cruise \n& Kongfjord' = "#ffddd2",'Not excluded' = "#caf0f8", 'Few otus' = "black"))+
  coord_cartesian(xlim = range(env_orig$x_coord), ylim= range(env_orig$y_coord))
```



# STUDY REGION - All
```{r}
# SPLIT<-"All"
# 
# otu<-otuSel_split[[SPLIT]][,-c(which(colnames(otuSel_split[[SPLIT]]) == "SampID"))]
# env<-envSel_split[[SPLIT]]
# 
# stations_sel <- rowSums(otu>0) > MinOTUs
# Sp_sel <- colSums(otu>0) > MinSightings
# 
# otu <- otu[stations_sel, Sp_sel]
# env <- env[stations_sel, ]
# env<-env[,colSums(is.na(env)>0) == 0]
```

```{r}
SPLIT<-"All"

otu<-otuSel_split[[SPLIT]][,-c(1)] #ncol(otuSel_split[[SPLIT]])
env<-envSel_split[[SPLIT]]

stations_sel <- rowSums(otu>0) > MinOTUs
Sp_sel <- colSums(otu>0) > MinSightings


otu <- otu[stations_sel, Sp_sel]
env <- env[stations_sel, ]

```

### ENV VAR chose
```{r}
# TRANSFORMATIONS 
env$log_bathy<-log(env$bathy*-1)
env$log_msr5_mag<-log(env$msr5_mag)
env$log_BO22_dissoxltmin_bdmean_n250<-log(env$BO22_dissoxltmin_bdmean-250)
env$sqrt_BO22_carbonphytomean_bdmean<-sqrt(env$BO22_carbonphytomean_bdmean)
env$Ice_PA<- ifelse(env$BO22_icethickmean_ss>0, "ICE", "NoICE")
env$Ice_PA<-as.factor(env$Ice_PA)

#Checking for covariation in predictor variables
ChosenEnvVar<- c("mud2",
                 "sand2",
                 "temp_mean",
                 "temp_std",
                 "salt_mean",
                 "log_bathy",
                 "log_msr5_mag",
                 "log_BO22_dissoxltmin_bdmean_n250")
pairs.panels(env[,ChosenEnvVar])
```

### TAXONOMY
```{r,fig.width= 8,fig.height = 30}
otu_sp<- ifelse(str_sub(colnames(otu),-3,-1) == "sp." , str_sub(colnames(otu), -str_length(colnames(otu)),-5), colnames(otu))
otu_sp<- gsub("[.]", "_", otu_sp)


temp_sp <-gsub(";", ".", Taxonomic_DF$Species)
temp_sp <-gsub("[ /]", "_", temp_sp)
temp_sp<-ifelse(str_sub(temp_sp,-3,-1) == "_sp", 
                str_sub(temp_sp, -str_length(temp_sp),-4),
                temp_sp)  

Taxonomic_DF<-Taxonomic_DF[temp_sp %in% otu_sp, ]

#### MAKE PHYLO TREE
Taxonomic_phylo<-as.phylo(~ Phylum/Subphylum/Superclass/Class/Subclass/Infraclass/Superorder/Order/Suborder/Infraorder/Superfamily/Family/Subfamily/Infrafamily/Genus/Species, data = Taxonomic_DF[3:ncol(Taxonomic_DF)], collapse = FALSE)
Taxonomic_phylo$edge.length<-rep(1, length(Taxonomic_phylo$edge))


#### Color Tree
Taxonomic_DF$class_colors<-NA
for(i in 1:length(unique(Taxonomic_DF$Class))){
  Taxonomic_DF$class_colors<-ifelse(Taxonomic_DF$Class ==   unique(Taxonomic_DF$Class)[i], 
                                    c(polychrome(), alphabet2())[i], Taxonomic_DF$class_colors)
}

Branch_col<-data.frame(Taxonomic_phylo$edge, "Branch_col"= NA, "Taxa" = NA)
for(i in 1:length(Taxonomic_phylo$tip.label)){
  if(i == 1){  
    Branch_col[1:which(Branch_col[,2] == i),3]<-Taxonomic_DF[i,ncol(Taxonomic_DF)]
    Branch_col[1:which(Branch_col[,2] == i),4]<-paste(Taxonomic_DF[i,"Class"])
    next}
  Branch_col[(which(Branch_col[,2] == (i-1))+1):which(Branch_col[,2] == i),3]<- Taxonomic_DF[Taxonomic_DF$Species == Taxonomic_phylo$tip.label[i], ncol(Taxonomic_DF)] # might need to change "Taxonomic_DF$Species" to "Taxonomic_DF$Subspecies" with the grab data
  
  Branch_col[(which(Branch_col[,2] == (i-1))+1):which(Branch_col[,2] == i),4]<- paste(Taxonomic_DF[Taxonomic_DF$Species == Taxonomic_phylo$tip.label[i], "Class"])
}
porifera_color<-Taxonomic_DF[Taxonomic_DF$Class == "Demospongiae",'class_colors'][1]
#bryozoa_color<-Taxonomic_DF[Taxonomic_DF$Phylum == "Bryozoa",'class_colors'][1]
Branch_col$Taxa<-ifelse(Branch_col$Taxa %in% Taxonomic_DF[Taxonomic_DF$Phylum == "Porifera", 'Class'], "Porifera", Branch_col$Taxa)
Branch_col$Taxa<-ifelse(Branch_col$Taxa %in% Taxonomic_DF[Taxonomic_DF$Phylum == "Bryozoa", 'Class'], "Bryozoa", Branch_col$Taxa)

Branch_col[Branch_col$Taxa == "Porifera", "Branch_col"]<-porifera_color
#Branch_col[Branch_col$Taxa == "Bryozoa", "Branch_col"]<-bryozoa_color


# PLOT tree
plot(Taxonomic_phylo, 
     edge.color= Branch_col$Branch_col)
legend("topleft",
       legend = unique(Branch_col[,3:4])[,2], #Name of groups
       col = unique(Branch_col[,3:4])[,1], # Color of the squares
       cex =.6, #sets legend size
       lwd=2, #sets line weight
       xpd=TRUE) #places outside plot area

```

# TRAITS
```{r}

Traits_orig<-read_excel(paste0(PathInputData,"/TraitsData.xlsx"), col_names = TRUE)
Traits_orig[!is.na(Traits_orig$Reference_List2) & Traits_orig$Reference_List2 == "Mycale_-Mycale-_lingua","Reference_List2"]<-"Mycale_lingua"

Traits_orig<-Traits_orig[Traits_orig$Reference_List2 %in% otu_sp,]

TraitsSel<-Traits_orig[,c('AphiaID', 'Reference_List2',
                          #   'Sociability_Solitary', 'Sociability_Gregarious', 
                          'Sociability_Colonial',"SociabilityGradient",
                          'Size_0_1','Size_1_2','Size_2_10','Size_10_20','Size_20_50','Size_50cm_',
                          'BodyType_Flat','BodyType_Mound','BodyType_Erect','BodyType_Other',
                          #'Larvae_Pelagic.planktotrophic.','Larvae_Pelagic.lecithtrophic.','Larvae_Benthic.DirectDevelopment.',
                          #'Reprod_AsexualBudding','Reprod_Sexual_BroadcastSpawnEggs','Reprod_Sexual_SeaBedEggs','Reprod_Sexual_BroodsEggs','Reprod_Hermaphrodite',
                          "Bioturb_Epifauna","Bioturb_SurfaceModifiers","Bioturb_UpwardConveyors","Bioturb_DownwardConveyors","Bioturb_BiodiffusiveMixers",
                          'Habit_TubeDwelling','Habit_BurrowDwelling','Habit_FreeLiving','Habit_CreviceDweller','Habit_Epi.endo_Zoic.phytic','Habit_Attached',
                          'Feed_SuspensionFilter','Feed_SurfaceDeposit','Feed_SubsurfaceDeposit','Feed_Scavenger','Feed_Predator',
                          'Mobility_Anchored','Mobility_PermanentAttached','Mobility_TemporaryAttached','Mobility_Sessile','Mobility_Swim','Mobility_Drifter','Mobility_Crawl',
                          'HabitatEffect_ReefBuilding','HabitatEffect_Bedforming')]



TraitsSel$BodyType<-colnames(TraitsSel[,which(colnames(TraitsSel) %in% c("BodyType_Flat", "BodyType_Mound", "BodyType_Erect"))])[max.col(TraitsSel[,which(colnames(TraitsSel) %in% c("BodyType_Flat", "BodyType_Mound", "BodyType_Erect"))],ties.method="first")]
TraitsSel[rowSums(TraitsSel[,which(colnames(TraitsSel) %in% c("BodyType_Flat", "BodyType_Mound", "BodyType_Erect"))]) < 2,'BodyType'] <- "Other"
TraitsSel[TraitsSel$BodyType %in% c("BodyType_Flat"),'BodyType']<-"Flat"
TraitsSel[TraitsSel$BodyType %in% c("BodyType_Mound"),'BodyType']<-"Mound"
TraitsSel[TraitsSel$BodyType %in% c("BodyType_Erect"),'BodyType']<-"Erect"


TraitsSel$Size<-NA
TraitsSel$Size<-colnames(TraitsSel[,which(colnames(TraitsSel) %in% c("Size_0_1","Size_1_2", "Size_2_10", "Size_10_20", "Size_20_50", "Size_50cm_"))])[max.col(TraitsSel[,which(colnames(TraitsSel) %in% c("Size_0_1","Size_1_2", "Size_2_10", "Size_10_20", "Size_20_50", "Size_50cm_"))],ties.method="first")]
TraitsSel[TraitsSel$Size %in% c("Size_0_1","Size_1_2", "Size_2_10"),'Size']<-"S"
TraitsSel[TraitsSel$Size %in% c("Size_10_20"),'Size']<-"M"
TraitsSel[TraitsSel$Size %in% c("Size_20_50"),'Size']<-"L"
TraitsSel[TraitsSel$Size %in% c("Size_50cm_"),'Size']<-"XL"

# TraitsSel[TraitsSel$Size_2_10>0 | TraitsSel$Size_10_20>0,'Size']<-"Medium"
# TraitsSel[TraitsSel$Size_20_50>0 | TraitsSel$Size_50cm_>0,'Size']<-"Large"

# TraitsSel$Larvae<-NA
# TraitsSel[TraitsSel$Larvae_Benthic.DirectDevelopment.>0,'Larvae']<-"None"
# TraitsSel[TraitsSel$Larvae_Pelagic.planktotrophic.>0,'Larvae']<-"Planktotrophic"
# TraitsSel[TraitsSel$Larvae_Pelagic.lecithtrophic.>0,'Larvae']<-"Lecithotrophic"
# TraitsSel[TraitsSel$Larvae_Pelagic.planktotrophic.>0 & TraitsSel$Larvae_Pelagic.lecithtrophic.>0,'Larvae']<-"Both"


# TraitsSel$Sociability<-colnames(TraitsSel[,3:5])[max.col(TraitsSel[,3:5],ties.method="first")]
# TraitsSel[TraitsSel$Sociability %in% c("Sociability_Solitary") ,'Sociability']<-"Solo"
# TraitsSel[TraitsSel$Sociability %in% c("Sociability_Gregarious") ,'Sociability']<-"Group"
#TraitsSel[TraitsSel$Sociability %in% c("Sociability_Colonial") ,'Sociability']<-"Colony"

TraitsSel[TraitsSel$Habit_Attached>0 |TraitsSel$Habit_Epi.endo_Zoic.phytic >0,'Habitat']<-"Attached"
TraitsSel$Habitat<-colnames(TraitsSel[,which(colnames(TraitsSel) %in% c("Habit_TubeDwelling", "Habit_BurrowDwelling", "Habit_FreeLiving", "Habit_CreviceDweller", "Habit_Epi.endo_Zoic.phytic", "Habit_Attached"))])[max.col(TraitsSel[,which(colnames(TraitsSel) %in% c("Habit_TubeDwelling", "Habit_BurrowDwelling", "Habit_FreeLiving", "Habit_CreviceDweller", "Habit_Epi.endo_Zoic.phytic", "Habit_Attached"))],ties.method="first")]
TraitsSel[TraitsSel$Habitat %in% c("Habit_Attached", "Habit_Epi.endo_Zoic.phytic") ,'Habitat']<-"Attached"
TraitsSel[TraitsSel$Habitat %in% c("Habit_BurrowDwelling" ,"Habit_TubeDwelling"),'Habitat']<-"TubeORBurrow"
TraitsSel[TraitsSel$Habitat == "Habit_FreeLiving" ,'Habitat']<-"Free"
TraitsSel[TraitsSel$Habitat == "Habit_CreviceDweller" ,'Habitat']<-"CreviceDweller"

TraitsSel$Mobility<-colnames(TraitsSel[,which(colnames(TraitsSel) %in% c("Mobility_Anchored","Mobility_PermanentAttached", "Mobility_TemporaryAttached", "Mobility_Sessile", "Mobility_Swim", "Mobility_Drifter", "Mobility_Crawl"))])[max.col(TraitsSel[,which(colnames(TraitsSel) %in% c("Mobility_Anchored","Mobility_PermanentAttached", "Mobility_TemporaryAttached", "Mobility_Sessile", "Mobility_Swim", "Mobility_Drifter", "Mobility_Crawl"))],ties.method="first")]
TraitsSel[TraitsSel$Mobility %in% c("Mobility_PermanentAttached", "Mobility_Sessile", "Mobility_Anchored") ,'Mobility']<-"Sessile"
TraitsSel[TraitsSel$Mobility %in% c("Mobility_TemporaryAttached") ,'Mobility']<-"TemporAttach"
 TraitsSel[TraitsSel$Mobility %in% c("Mobility_Crawl") ,'Mobility']<-"Crawl"
# TraitsSel[TraitsSel$Mobility %in% c("Mobility_Crawl", "Mobility_Drifter") ,'Mobility']<-"Medium"
TraitsSel[TraitsSel$Mobility %in% c("Mobility_Swim") ,'Mobility']<-"Swim"



TraitsSel$Feeding<-colnames(TraitsSel[,which(colnames(TraitsSel) %in% c("Feed_SuspensionFilter","Feed_SurfaceDeposit","Feed_SubsurfaceDeposit","Feed_Scavenger","Feed_Predator"))])[max.col(TraitsSel[,which(colnames(TraitsSel) %in% c("Feed_SuspensionFilter","Feed_SurfaceDeposit","Feed_SubsurfaceDeposit","Feed_Scavenger","Feed_Predator"))],ties.method="first")]
TraitsSel[TraitsSel$Feeding %in% c("Feed_Scavenger","Feed_Predator") ,'Feeding']<-"PredatorScavenger"
TraitsSel[TraitsSel$Feeding %in% c("Feed_SubsurfaceDeposit","Feed_SurfaceDeposit") ,'Feeding']<-"Surface"
TraitsSel[TraitsSel$Feeding %in% c("Feed_SuspensionFilter") ,'Feeding']<-"Suspension"


TraitsSel$Bioturbation<-colnames(TraitsSel[,which(colnames(TraitsSel) %in% c("Bioturb_Epifauna","Bioturb_SurfaceModifiers","Bioturb_UpwardConveyors","Bioturb_DownwardConveyors","Bioturb_BiodiffusiveMixers"))])[max.col(TraitsSel[,which(colnames(TraitsSel) %in% c("Bioturb_Epifauna","Bioturb_SurfaceModifiers","Bioturb_UpwardConveyors","Bioturb_DownwardConveyors","Bioturb_BiodiffusiveMixers"))],ties.method="first")]
TraitsSel[TraitsSel$Bioturbation %in% c("Bioturb_Epifauna") ,'Bioturbation']<-"Epifauna"
TraitsSel[TraitsSel$Bioturbation %in% c("Bioturb_SurfaceModifiers") ,'Bioturbation']<-"SurfaceModifier"
TraitsSel[TraitsSel$Bioturbation %in% c("Bioturb_UpwardConveyors", "Bioturb_DownwardConveyors") ,'Bioturbation']<-"UpDownConveyor"
TraitsSel[TraitsSel$Bioturbation %in% c("Bioturb_BiodiffusiveMixers") ,'Bioturbation']<-"BiodiffusiveMixer"



TraitsSel$Colonial<-ifelse(TraitsSel$Sociability_Colonial>0, "Col", "Ind")

#  TraitsSel$Sensitivity<-colnames(TraitsSel[,40:43])[max.col(TraitsSel[,40:43],ties.method="first")]

plot_si<-ggplot(TraitsSel)+geom_bar(aes("Size",fill = Size))+theme_classic()+theme(axis.title =  element_blank(),legend.position = "bottom", legend.direction="vertical")
plot_bt<-ggplot(TraitsSel)+geom_bar(aes("Body type",fill = BodyType))+theme_classic()+theme(axis.title =  element_blank(),legend.position = "bottom", legend.direction="vertical")
#plot_he<-ggplot(TraitsSel)+geom_bar(aes("Habitat effect",fill = HabitatEffect))+theme_classic()+theme(axis.title =  element_blank(),legend.position = "bottom", legend.direction="vertical")
#plot_l<-ggplot(TraitsSel)+geom_bar(aes("Larvae",fill = Larvae))+theme_classic()+theme(axis.title =  element_blank(),legend.position = "bottom", legend.direction="vertical")
plot_h<-ggplot(TraitsSel)+geom_bar(aes("Habitat",fill = Habitat))+theme_classic()+theme(axis.title =  element_blank(),legend.position = "bottom", legend.direction="vertical")
plot_m<-ggplot(TraitsSel)+geom_bar(aes("Mobility",fill = Mobility))+theme_classic()+theme(axis.title =  element_blank(),legend.position = "bottom", legend.direction="vertical")
plot_f<-ggplot(TraitsSel)+geom_bar(aes("Feeding",fill = Feeding))+theme_classic()+theme(axis.title =  element_blank(),legend.position = "bottom", legend.direction="vertical")
plot_sp<-ggplot(TraitsSel)+geom_bar(aes("Sociability",fill = as.factor(SociabilityGradient)))+theme_classic()+theme(axis.title =  element_blank(),legend.position = "bottom", legend.direction="vertical")
plot_tur<-ggplot(TraitsSel)+geom_bar(aes("Bioturbation",fill = Bioturbation))+theme_classic()+theme(axis.title =  element_blank(),legend.position = "bottom", legend.direction="vertical")

plot_col<-ggplot(TraitsSel)+geom_bar(aes("Colonial",fill = as.factor(Colonial)))+theme_classic()+theme(axis.title =  element_blank(),legend.position = "bottom", legend.direction="vertical")


#ggarrange(plot_si,plot_bt,plot_he,plot_l,plot_h,plot_m,plot_f,plot_sp)
plot_si
plot_bt
#plot_he
#plot_l
plot_h
plot_m
plot_f
plot_sp
plot_tur
plot_col


traits<-TraitsSel
rownames(traits)<-traits$Reference_List2

traits<-traits[match(colnames(otu), row.names(traits)),]
```


```{r}
otu$SampID <- env$SampID
save(traits, file = paste0(PathOutput,"traits_",SPLIT,".rda"))
save(Taxonomic_phylo, file = paste0(PathOutput,"Taxonomic_phylo_",SPLIT,".rda"))
save(Branch_col, file = paste0(PathOutput,"Branch_col_",SPLIT,".rda"))
save(Taxonomic_DF, file = paste0(PathOutput,"Taxonomic_DF",SPLIT,".rda"))
save(otu, file = paste0(PathOutput,"otu_Video_",SPLIT,".rda"))
save(env, file =paste0(PathOutput,"env_Video_",SPLIT,".rda"))
```



```{r,out.width="50%", fig.height = 15 }
rHarvestEffort_df<-as.data.frame(rHarvestEffort$AllRelativeEffort, xy = TRUE)
rHarvestEffort_df<-rHarvestEffort_df[!is.na(rHarvestEffort_df$AllRelativeEffort),]

ggplot() +  
  geom_tile(data=rHarvestEffort_df, aes(x=x, y=y, fill=round(AllRelativeEffort)), alpha=0.8) + 
  scale_fill_gradientn(colors = c('white', '#4cc9f0', "#3a0ca3", "#f72585"), na.value = NA) +
  geom_point(data = env, aes(x_coord, y_coord, color = Trawling), size = 5, alpha = 0.3)+
  scale_color_gradientn(colors = c('white', '#ffff3f', "#80b918", "#43291f"), na.value = NA) +
  theme_classic()+
  coord_cartesian(xlim = c(-100000,1300000), ylim = c(6500000, 9000000))+
  geom_map(data =  ggworldMap, map = ggworldMap, aes(long, lat, map_id = id), fill = "#ddb892", alpha = 0.2)
```