---
title: "Video_DataPrep"
output: html_document
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

# PACKAGES
```{r, message=FALSE, warning=FALSE}
 library(dplyr)
 library(openxlsx)
 library(ggplot2)
 library(psych)
 library(stringr)
 library(pals)
 library(oce) # To estimate water density
 library(reshape2)

set.seed(6) # At one point I "randomly "chose" stations within some Rstations. This makes sure that the random selection stays equal to allow replicability among us. 
```

# PATHS and other funcitons
```{r, message=FALSE, warning=FALSE}
PathScripts<-"C:/Users/a39495/Documents/Projects/MAREANO/MAREANO_Video/"
PathInputData<-"C:/Users/a39495/Havforskningsinstituttet/MAREANO Biotope modelling - VideoData/Input/"
PathOutput<- "C:/Users/a39495/Havforskningsinstituttet/MAREANO Biotope modelling - VideoData/Output/"
PathTaxonary<-"C:/Users/a39495/Havforskningsinstituttet/Video analysis lab - Reference List/Taxonary.xlsx"
source(paste0(PathScripts, "MY_TaxonomicFromWormsDF.r"))
source(paste0(PathScripts, "VME_Spp.r")) # I add this to make sure VME species are kepts even if they are below "MinSightings"
#=======
PathScripts<-"C:/Users/a21448/Havforskningsinstituttet/MAREANO Biotope modelling - General/VideoData/Scripts/"
PathInputData<-"C:/Users/a21448/Havforskningsinstituttet/MAREANO Biotope modelling - General/VideoData/Input/"
PathOutput<- "C:/Users/a21448/Havforskningsinstituttet/MAREANO Biotope modelling - General/VideoData/Output/"

#source(paste0(PathScripts, "MY_TaxonomicFromWormsDF.r"))
source("MY_TaxonomicFromWormsDF.r")
```

# MCMC options
```{r}
MinOTUs<- 0
MinSightings<- 20
```

# Land geography
```{r, message=FALSE}
load(paste0(PathInputData,"worldMap.rda"))
ggworldMap<-fortify(worldMap)
```
# LOAD DATA

## -Trawling
Loads trawling data
```{r, warning=FALSE, message=FALSE}
if(FALSE){
  FishingEffort<-read.csv(paste0(PathInputData,"effort_fish.csv"), sep = ",")
  ShrimpingEffort<-read.csv(paste0(PathInputData,"effort_shrimp.csv"), sep = ",")
  
  FishingEffort[log(FishingEffort$Val_meankwHour+1)<5,'RelativeEffort']<-0
  FishingEffort[log(FishingEffort$Val_meankwHour+1)>=5 & log(FishingEffort$Val_meankwHour+1) <8.7,'RelativeEffort']<-1
  FishingEffort[log(FishingEffort$Val_meankwHour+1)>=8.7 & log(FishingEffort$Val_meankwHour+1) <10,'RelativeEffort']<-2
  FishingEffort[log(FishingEffort$Val_meankwHour+1)>=10 ,'RelativeEffort']<-3
  
  hist(log(FishingEffort$Val_meankwHour[FishingEffort$Val_meankwHour!= 0 ]), breaks =100)
  abline(v=5, col="blue")
  abline(v=8.7, col="orange")
  abline(v=10, col="red")
  
  ShrimpingEffort[log(ShrimpingEffort$Val_meankwHour+1)<5,'RelativeEffort']<-0
  ShrimpingEffort[log(ShrimpingEffort$Val_meankwHour+1)>=5 & log(ShrimpingEffort$Val_meankwHour+1) <7.9,'RelativeEffort']<-1
  ShrimpingEffort[log(ShrimpingEffort$Val_meankwHour+1)>=7.9 & log(ShrimpingEffort$Val_meankwHour+1) <8.9,'RelativeEffort']<-2
  ShrimpingEffort[log(ShrimpingEffort$Val_meankwHour+1)>=8.9 ,'RelativeEffort']<-3
  
  hist(log(ShrimpingEffort$Val_meankwHour[ShrimpingEffort$Val_meankwHour!= 0 ]), breaks =100)
  abline(v=5, col="blue")
  abline(v=7.9, col="orange")
  abline(v=8.9, col="red")
  
  FishingEffort$AllRelativeEffort<-pmax(FishingEffort$RelativeEffort, ShrimpingEffort$RelativeEffort)
  
  rHarvestEffort<-rasterFromXYZ(FishingEffort[,c(2,1,6)]) 
  
  proj4string(rHarvestEffort)<-sp::CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")
  rHarvestEffort <- projectRaster(rHarvestEffort, crs = "+proj=utm +ellps=WGS84 +zone=33 +datum=WGS84")
  
  rHarvestEffort@data@values<-round(rHarvestEffort@data@values)
  plot(rHarvestEffort)
}
load(paste0(PathInputData,"rHarvestEffort_raster.rda")) # loads rHarvestEffort
```

## -Env
```{r, warning=FALSE}
env_orig <- read.csv(paste0(PathInputData,"envData_2023-07-21.csv")) %>% as.data.frame
env_orig<-unique(env_orig)
env_orig[sapply(env_orig, is.character)] <- lapply(env_orig[sapply(env_orig, is.character)], as.factor)

samp_info <- read.csv(paste0(PathInputData,"sample_info.csv")) %>% as.data.frame
samp_info<-samp_info[!(duplicated(samp_info$SampID)),]
env_orig<-merge(env_orig, samp_info, by = "SampID", all.x = TRUE)

## Removing some env variables that I dont use and which were giving issues because they contain NAs
env_orig <- env_orig %>% dplyr::select(-c(spd_std, slope9, BO22_lightbotltmax_bdmean, BO22_lightbotltmin_bdmean, BO22_lightbotmean_bdmean, BO22_lightbotrange_bdmean))
```

## -Bio
```{r, warning=FALSE}
otu_orig <- read.csv(paste0(PathInputData,"species_densities.csv")) %>% as.data.frame
otu_orig <- dcast(otu_orig, SampID ~ clean_taxonomy, value.var="density_n100m2")
otu_orig[is.na(otu_orig)]<-0
```

## - Taxon
```{r, warning=FALSE}
Taxonary<-read.xlsx(PathTaxonary , sheet = 1)
Taxonary$Reference.List2 <-gsub(";", ".", Taxonary$Reference_List)
Taxonary$Reference.List2 <-gsub("[ /]", "_", Taxonary$Reference.List2)
```

Filter out taxa:
- Small taxa
- Plants and other non-animals
```{r, warning=FALSE}
otu_orig<-otu_orig[,c(TRUE, colnames(otu_orig)[-1] %in% Taxonary[
  Taxonary$Size_class %in% c("OK", "Detailed") & 
    Taxonary$Specificity<4 & 
    Taxonary$Object_type == "Organism" & 
    Taxonary$Ecosystem_section != "Pelagic" &
    !(Taxonary$Grouping_taxon_biotope %in% c("Algae", "Bacteria", "Biota", "Foraminifera"))  ,'Reference_List'])]
```

# JOIN DATASETS 
Join the different data sets to make them match and filter out some stations based on:
- minimum length
- minimum vision 
- 2006 cruise removed
- stations that produced errors in the latent autocorrelation estimation (neighbouring stations with very different species patters)
```{r, warning=FALSE}
joinedDat<- left_join(otu_orig,env_orig, by="SampID")
joinedDat<-joinedDat[!is.na(joinedDat$SampID),]
joinedDat<-joinedDat[joinedDat$SegLengthM>190 & joinedDat$SegLengthM < 300,]
joinedDat<-joinedDat[is.na(joinedDat$no_vision) | rowSums(joinedDat[,c('no_vision','poor_vision')], na.rm = TRUE) <0.5 | is.na(joinedDat$poor_vision),]
joinedDat<-joinedDat[joinedDat$cruise_no != "2006612",]

#Removes sites too close to each other
joinedDat<-joinedDat[!(joinedDat$VL %in% c('779', '624','1222', '2113', '927','183','1888','2099','623', '1951','161','2136', '785', '1940', '2172', '1869', '2173','166', '578','821' )),]
```

# SEPARATE 
Separate the now matching datasets (joinedDat -> otu_sort + env_sort)
```{r, warning=FALSE}
#Takes one random 200m transect from each station
joinedDat<-joinedDat %>%
  dplyr::group_by(VL)%>%
  dplyr::slice_sample(n=1) %>%
  ungroup()

#replaces hard coded column selection
otu_sort<- joinedDat %>% dplyr::select(c(1,which(colnames(joinedDat)== "SampID2"), 2:which(colnames(joinedDat)==names(otu_orig)[ncol(otu_orig)])))
env_sort<-joinedDat %>% dplyr::select(c(1, (which(colnames(joinedDat)==names(otu_orig)[ncol(otu_orig)])+1):ncol(joinedDat)))
```

### Data cleaning
Make sure that all env data variables are complete (cannot have NAs in the environmental data)
```{r}
ChosenEnvVar<- c("mud","sand", "Tmean_Robinson","bathy", "BO22_dissoxltmin_bdmean")
## Removing NAs
otuCompl <- otu_sort[complete.cases(env_sort[, c("x_coord", "y_coord","cruise_no",ChosenEnvVar )]), ]
envCompl <- env_sort[complete.cases(env_sort[,  c("x_coord", "y_coord","cruise_no",ChosenEnvVar )]), ]
envCompl$Trawling<-extract(rHarvestEffort, envCompl[,c('x_coord', 'y_coord')])

# Remove species with 0 records
otuCompl<-otuCompl %>% select_if(~ !is.numeric(.) || sum(.) != 0) 
```


Remove  otu
```{r}
#Remove species
otuCompl<-otuCompl[,-which(colnames(otuCompl) %in% c("SampID2", 
                                                     "Polychaeta errantia",
                                                     "Polychaeta fishingnet", 
                                                     "Polychaeta sediment tube", 
                                                     "Polychaeta question mark",
                                                     "Polychaeta sedentaria",
                                                     "Polychaeta errantia",
                                                     "Polychaeta soft thin tube",
                                                     "Polychaeta tube",
                                                     "Cup coral"#, # This one gets lost in the taxonomic functions because it is not associated to any toxonomic valid name
                                                     ))]

# Taxonary$Reference.List3<- ifelse(str_sub(Taxonary$Reference.List2,-3,-1) == "sp." , str_sub(Taxonary$Reference.List2, -str_length(Taxonary$Reference.List2),-5), Taxonary$Reference.List2)
# otu_sp<- ifelse(str_sub(colnames(otu),-3,-1) == "sp." , str_sub(colnames(otu), -str_length(colnames(otu)),-5), colnames(otu))
# Taxonary[which(Taxonary$Reference.List3 %in% otu_sp),]

 # XXX <-gsub("[ ;]", " ", colnames(otuCompl))
 # XXX <-gsub("[.]", "", XXX)
```

Results in a data set that contains information on which species could be summed with otus of coarser resolution. This is done to improve predictions of those coarser resolution otus, which in turn might help improve prediction strength on the finer resolutions

```{r}
#Takes otuCompl
source(paste0(PathScripts,"TaxonomyAggregate.r")) 
# Gives Taxonomic_DF_Groups
levels(Taxonomic_DF_Groups$Species)[levels(Taxonomic_DF_Groups$Species) == "Echinoidea irregular"] <- "Irregularia"
levels(Taxonomic_DF_Groups$Species)[levels(Taxonomic_DF_Groups$Species) == "Echinoidea regular"] <- "Carinacea"

#XXX[which(!(XXX %in% Taxonomic_DF_Groups$Species)) ]
```

Sums observations of finer resoltuions to the higher resolutions
```{r}
otuCompl_Sum<-otuCompl
for(i in 2:ncol(otuCompl)){
  
  TargetSp<-colnames(otuCompl)[i]
  TargetSp<-ifelse(str_sub(TargetSp,-3,-1) == "sp.", str_sub(TargetSp,-str_length(TargetSp),-5), TargetSp)
  
  # otus indicating multiple possible species are flaged and treated different to simple coarser resolutions otus
  if(TargetSp %in% c("Ceramaster_Hippasterias", "Porania_Poraniomorpha" ,"Bythocaris_Boreomysis", "Lycodonus_Lycenchelys_Lumpenus", "Lycodonus_Lycenchelys","Phakellia_Axinella","Geodia_Stryphnus","Geodia_Stelleta")){
    MultiSp<-unlist(str_split(TargetSp, "_"))    
    if(any(MultiSp %in% "Hippasterias")){MultiSp<- c("Ceramaster", "Hippasteria")}
    XXX<-Taxonomic_DF_Groups %>% dplyr::select(which(colnames(Taxonomic_DF_Groups) == "Genus"):ncol(Taxonomic_DF_Groups)) %>% filter_all(any_vars(. %in% MultiSp))
    
  }else{
    if(TargetSp == "Echinoidea_regular"){TargetSp<-"Carinacea"}
    if(TargetSp == "Echinoidea_irregular"){TargetSp<-"Irregularia"}

    XXX<-Taxonomic_DF_Groups %>% dplyr::select(which(colnames(Taxonomic_DF_Groups) == "Species"):ncol(Taxonomic_DF_Groups)) %>% filter_all(any_vars(. %in% c(TargetSp)))
  }
  
  OtherSp<-XXX$Species[XXX$Species != TargetSp]
  if(length(OtherSp) == 0){next}
  
  print(paste(TargetSp,"gets:")) 
  print(paste(OtherSp))
  
  temp_sp <-gsub(";", ".", c(colnames(otuCompl)[i],paste(OtherSp)))
  temp_sp <-gsub("[ /]", "_", temp_sp)
  temp_sp<-ifelse(str_sub(temp_sp,-2,-1) == "sp", paste0(temp_sp, "."), temp_sp)  
  
  otuCompl_Sum[,paste0(TargetSp, "_Summed")]<-rowSums(otuCompl_Sum[,which(colnames(otuCompl_Sum) %in% temp_sp)])
}
otuCompl_Sum<-otuCompl_Sum %>% dplyr::select(-c(Bythocaris_Summed)) 
otuCompl_Sum$Porania_Summed <- rowSums(otuCompl_Sum[,which(colnames(otuCompl_Sum) %in% c("Porania_pulvillus", "Porania_sp."))])
```

Grouping of additional entries based on morphology/color
```{r}
# PORIFERA
Taxonary[Taxonary$Reference_List %in% c("Porifera encrusting;bluegrey", "Porifera encrusting;brown","Porifera encrusting;green","Porifera encrusting;grey","Porifera encrusting;orange","Porifera encrusting;purple", "Porifera encrusting;red","Porifera encrusting;white", "Porifera encrusting;yellow", "Halichondria sp."), 'Analysis_name']<-"Porifera encrusting"
Taxonary[Taxonary$Reference_List %in% c("Porifera medium;white","Porifera medium;yellow"), 'Analysis_name']<-"Porifera medium"
Taxonary[Taxonary$Reference_List %in% c("Porifera small;irregular","Porifera small;orange","Porifera small;white","Porifera small;yellow", "Porifera small;spikey", "Porifera small;green", "Porifera urn", "Grantia compressa"), 'Analysis_name']<-"Porifera small"
Taxonary[Taxonary$Reference_List %in% c("Porifera small;round yellow", "Porifera cupcake",  "Porifera_window", "Tetilla sp.", "Tentorium semisuberites"), 'Analysis_name']<-"Porifera small round"
Taxonary[Taxonary$Reference_List %in% c("Porifera lollipop", "Porifera lily", "Halichondria sp.", "Hyalonema sp.","Sycon stalked", "Sycon sp.", "Hyalonema sp."), 'Analysis_name']<-"Porifera small;stalked"
Taxonary[Taxonary$Reference_List %in% c("Porifera bat"), 'Analysis_name']<-"Porifera erect"
Taxonary[Taxonary$Reference_List %in% c("Porifera brown papillae", "Polymastia sp.", "Weberella bursa","Polymastia grimaldii"), 'Analysis_name']<-"Polymastiidae"
Taxonary[Taxonary$Reference_List %in% c("Porifera white bush"), 'Analysis_name']<-"Porifera branched"
Taxonary[Taxonary$Reference_List %in% c("Porifera fan;big","Porifera fan;white", "Porifera fan;small","Plicatellopsis bowerbanki"), 'Analysis_name']<-"Porifera fan"
Taxonary[Taxonary$Reference_List %in% c("Primnoa resedaeformis;impacted"), 'Analysis_name']<-"Primnoa resedaeformis" 
Taxonary[Taxonary$Reference_List %in% c("Paragorgia arborea;impacted"), 'Analysis_name']<-"Paragorgia arborea"
 
FixThese<-c("Porifera encrusting","Porifera medium" ,"Porifera small","Porifera small round","Porifera small;stalked","Porifera small;stalked","Porifera erect","Porifera branched","Polymastiidae","Porifera fan","Primnoa resedaeformis" ,"Paragorgia arborea")

for(i in 1:length(FixThese)){
  From<-Taxonary[!is.na(Taxonary$Analysis_name) & Taxonary$Analysis_name %in% FixThese[i],'Reference.List2']
  To<-Taxonary[Taxonary$Reference_List == FixThese[i],'Reference.List2']
  
  if(any(colnames(otuCompl) %in% From)){
    if(any(colnames(otuCompl) %in% To)){
      otuCompl[,To]<-rowSums(otuCompl[,which(colnames(otuCompl) %in% c(To, From))]) # sums densities of all species with same "analyses name"
    }
  }
}
```

"otuCompl_Sum" currently contains columns with the unsummed and the summed coarser taxonomic resolutions. We  remove the unsummed. We also remove these unsumed in the "otuCompl" (which had the summed morphotypes) data frame and combine the columns to end up with a data frame containing summed morphotypes and summed taxonomies.
```{r}
# Taxonomic resolutions summed dataset 
tempdf<-otuCompl_Sum[,which(!(colnames(otuCompl_Sum) %in% colnames(otuCompl)))]
colnames(tempdf)<- str_sub(colnames(tempdf),-str_length(colnames(tempdf)) ,-8) # Removeds the "_Summed" part of the string

# Morphotypes fix summed dataset 
otuCompl<-otuCompl[, which(!(colnames(otuCompl) %in% c(colnames(tempdf),paste0(colnames(tempdf),"_sp."))))]

# Merge fixed datasets
otuCompl<-cbind(otuCompl, tempdf)
#Remove old morphotypes
otuCompl<-otuCompl[,which(!(colnames(otuCompl) %in% c("Actiniaria.red","Actiniaria.violet","Actiniaria_buried.redish","Actiniaria.orange","Actiniaria.pink","Actiniaria.white","Actiniaria.yellow",
                                                      "Cerianthidae.dark","Cerianthidae.violet",
                                                      "Asteroidea.orange", "Asteroidea.white",
                                                      "Bryozoa_calcareous_branched","Bryozoa_coral",                                                      "Porifera_encrusting.bluegrey","Porifera_encrusting.green","Porifera_encrusting.grey","Porifera_encrusting.orange","Porifera_encrusting.purple", "Porifera_encrusting.white", "Porifera_encrusting.yellow",  "Porifera_fan.white","Porifera_medium_round","Porifera_medium.white" ,"Porifera_medium.yellow",    "Porifera_small.irregular","Porifera_small.round_yellow", "Porifera_small.white", "Porifera_small.yellow", "Porifera_bat", "Porifera_lollipop", "Porifera_lily")))]
```


Subsets based on thresholds:
  -Species with a minimum number of occurrences
  -Stations with the minimum number of species and 
```{r}
# Removes species with less than "MinSightings" that are not VMEs
Sp_sel <- c(TRUE, colSums(otuCompl[, -c(1)]>0) > MinSightings)
Sp_sel[which(colnames(Sp_sel) %in% c(ALL_vme))]<-TRUE

stations_sel <- rowSums(otuCompl[, -c(1)]>0) > MinOTUs

otuSel <- otuCompl[stations_sel, Sp_sel]
envSel <- envCompl[stations_sel, ]

envSel$swDensRob_avs<-swRho(salinity=envSel$Smean_Robinson,
                              temperature=envSel$Tmean_Robinson,
                              pressure=(envSel$bathy*-1),
                              eos="unesco")


envSel<-envSel[ , colSums(is.na(envSel))==0] #Remove environmental variables with NAs
envSel$SampID<-as.factor(envSel$SampID)
```


# SPLITS
```{r, warning=FALSE, fig.width= 10,fig.height = 10}
envSel_split<-list()
otuSel_split<-list()

# StudyRegion<-envSel[envSel$bathy < -495  & envSel$bathy<=-100 & envSel$SampID != "345_02",  'SampID']
# envSel_split[["Deep"]]<-envSel[envSel$SampID  %in%  StudyRegion$SampID,]
# otuSel_split[["Deep"]]<-otuSel[otuSel$SampID %in%  StudyRegion$SampID,]
# 
# StudyRegion<-envSel[envSel$bathy > -495  & envSel$BO22_dissoxmean_bdmean > 305 & envSel$bathy<=-100,  'SampID']
# envSel_split[["Barents"]]<-envSel[envSel$SampID  %in%  StudyRegion$SampID,]
# otuSel_split[["Barents"]]<-otuSel[otuSel$SampID %in%  StudyRegion$SampID,]
# 
# StudyRegion<-envSel[envSel$bathy > -495  & envSel$BO22_dissoxmean_bdmean <= 305 & envSel$bathy<=-100 & envSel$BO22_icecoverrange_ss == 0,  'SampID']
# envSel_split[["Shelf"]]<-envSel[envSel$SampID  %in%  StudyRegion$SampID,]
# otuSel_split[["Shelf"]]<-otuSel[otuSel$SampID %in%  StudyRegion$SampID,]
# 

StudyRegion<-envSel[envSel$bathy<=-100 & envSel$SampID != "345_02",  'SampID']
envSel_split[["All"]]<-envSel[envSel$SampID  %in% StudyRegion$SampID,]
otuSel_split[["All"]]<-otuSel[otuSel$SampID %in% StudyRegion$SampID,]


ggplot()+
  geom_point(data = env_orig[rowSums(env_orig[,c('no_vision','poor_vision')], na.rm = TRUE) > 0.5,], aes(x_coord, y_coord, color = "Poor vision"), alpha = 0.5, size = 1)+
  geom_point(data = env_orig[env_orig$SegLength< 190,], aes(x_coord, y_coord, color = "Too short"), alpha = 0.5, size = 1)+
  geom_point(data = env_orig[env_orig$SegLength> 300,], aes(x_coord, y_coord, color = "Too long"), alpha = 0.5, size = 1)+

  geom_point(data = env_orig[env_orig$bathy > -100,], aes(x_coord, y_coord, color = "Too shallow"), alpha = 0.5, size = 1)+
  geom_point(data = env_orig[env_orig$cruise_no  == "2006612",], aes(x_coord, y_coord, color = "2006 cruise"), alpha = 0.5, size = 1)+
  geom_point(data = envSel_split[["All"]], aes(x_coord, y_coord, color = "Not excluded"), size = 1)+
  geom_map(data =  ggworldMap, map = ggworldMap, aes(long, lat, map_id = id), fill = "#ddb892", alpha = 0.2)+
  theme_void()+
  scale_color_manual(name='Stations excluded',
                     breaks=c('Poor vision', 'Too short','Too long', 'Too shallow', '2006 cruise','Not excluded'),
                     values=c('Poor vision' = "#e9c46a", 'Too short' = "#e76f51", 'Too long' = "#9c89b8", 'Too shallow' = "#2a9d8f", '2006 cruise' = "#ffddd2",'Not excluded' = "#caf0f8"))+
  coord_cartesian(xlim = range(env_orig$x_coord), ylim= range(env_orig$y_coord))
```



# STUDY REGION - All
```{r}
SPLIT<-"All"

otu<-otuSel_split[[SPLIT]][,-c(which(colnames(otuSel_split[[SPLIT]]) == "SampID"))]
env<-envSel_split[[SPLIT]]

stations_sel <- rowSums(otu>0) > MinOTUs
Sp_sel <- colSums(otu>0) > MinSightings

otu <- otu[stations_sel, Sp_sel]
env <- env[stations_sel, ]
```


### ENV VAR chose
```{r}
# TRANSFORMATIONS 
env$log_bathy<-log(env$bathy*-1)
env$sqrt_BO22_carbonphytomean_bdmean<-sqrt(env$BO22_carbonphytomean_bdmean)
env$Ice_PA<- ifelse(env$BO22_icethickmean_ss>0, "ICE", "NoICE")
env$Ice_PA<-as.factor(env$Ice_PA)

#Checking for covariation in predictor variables
ChosenEnvVar<- c("mud",
                 "sand",
                 "Tmean_Robinson",
                 "log_bathy",
                 "BO22_dissoxltmin_bdmean",
                 "msr5_mag",
                 "Smean_Robinson",
                 "Ssd_Robinson")
pairs.panels(env[,ChosenEnvVar])
```

### TAXONOMY
```{r,fig.width= 8,fig.height = 30}
otu_sp<- ifelse(str_sub(colnames(otu),-3,-1) == "sp." , str_sub(colnames(otu), -str_length(colnames(otu)),-5), colnames(otu))
otu_sp<- gsub("[.]", "_", otu_sp)


temp_sp <-gsub(";", ".", Taxonomic_DF$Species)
temp_sp <-gsub("[ /]", "_", temp_sp)
temp_sp<-ifelse(str_sub(temp_sp,-3,-1) == "_sp", 
str_sub(temp_sp, -str_length(temp_sp),-4),
 temp_sp)  

Taxonomic_DF<-Taxonomic_DF[temp_sp %in% otu_sp, ]

#### MAKE PHYLO TREE
Taxonomic_phylo<-as.phylo(~ Phylum/Subphylum/Superclass/Class/Subclass/Infraclass/Superorder/Order/Suborder/Infraorder/Superfamily/Family/Subfamily/Infrafamily/Genus/Species, data = Taxonomic_DF[3:ncol(Taxonomic_DF)], collapse = FALSE)
Taxonomic_phylo$edge.length<-rep(1, length(Taxonomic_phylo$edge))


#### Color Tree
Taxonomic_DF$class_colors<-NA
for(i in 1:length(unique(Taxonomic_DF$Class))){
  Taxonomic_DF$class_colors<-ifelse(Taxonomic_DF$Class ==   unique(Taxonomic_DF$Class)[i], 
                                    c(polychrome(), alphabet2())[i], Taxonomic_DF$class_colors)
}

Branch_col<-data.frame(Taxonomic_phylo$edge, "Branch_col"= NA, "Taxa" = NA)
for(i in 1:length(Taxonomic_phylo$tip.label)){
  if(i == 1){  
    Branch_col[1:which(Branch_col[,2] == i),3]<-Taxonomic_DF[i,ncol(Taxonomic_DF)]
    Branch_col[1:which(Branch_col[,2] == i),4]<-paste(Taxonomic_DF[i,"Class"])
    next}
  Branch_col[(which(Branch_col[,2] == (i-1))+1):which(Branch_col[,2] == i),3]<- Taxonomic_DF[Taxonomic_DF$Species == Taxonomic_phylo$tip.label[i], ncol(Taxonomic_DF)] # might need to change "Taxonomic_DF$Species" to "Taxonomic_DF$Subspecies" with the grab data
  
  Branch_col[(which(Branch_col[,2] == (i-1))+1):which(Branch_col[,2] == i),4]<- paste(Taxonomic_DF[Taxonomic_DF$Species == Taxonomic_phylo$tip.label[i], "Class"])
}
porifera_color<-Taxonomic_DF[Taxonomic_DF$Class == "Demospongiae",'class_colors'][1]
bryozoa_color<-Taxonomic_DF[Taxonomic_DF$Phylum == "Bryozoa",'class_colors'][1]
Branch_col$Taxa<-ifelse(Branch_col$Taxa %in% Taxonomic_DF[Taxonomic_DF$Phylum == "Porifera", 'Class'], "Porifera", Branch_col$Taxa)
Branch_col$Taxa<-ifelse(Branch_col$Taxa %in% Taxonomic_DF[Taxonomic_DF$Phylum == "Bryozoa", 'Class'], "Bryozoa", Branch_col$Taxa)

Branch_col[Branch_col$Taxa == "Porifera", "Branch_col"]<-porifera_color
Branch_col[Branch_col$Taxa == "Bryozoa", "Branch_col"]<-bryozoa_color


# PLOT tree
plot(Taxonomic_phylo, 
     edge.color= Branch_col$Branch_col)
legend("topleft",
       legend = unique(Branch_col[,3:4])[,2], #Name of groups
       col = unique(Branch_col[,3:4])[,1], # Color of the squares
       cex =.6, #sets legend size
       lwd=2, #sets line weight
       xpd=TRUE) #places outside plot area

```


```{r}
save(Taxonomic_phylo, file = paste0(PathOutput,"Taxonomic_phylo_",SPLIT,".rda"))
save(Branch_col, file = paste0(PathOutput,"Branch_col_",SPLIT,".rda"))
save(Taxonomic_DF, file = paste0(PathOutput,"Taxonomic_DF",SPLIT,".rda"))

save(otu, file = paste0(PathOutput,"otu_Video_",SPLIT,".rda"))
save(env, file =paste0(PathOutput,"env_Video_",SPLIT,".rda"))
```


